How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-04-22 Paper/paper.tex
Changes recursive loops to loops

\begin{table*}[ht]
	\centering
	\begin{tabular}{lrrrrrr}
		\hline
		&\textbf{mean}&\textbf{min}&\textbf{Q1}&\textbf{median}&\textbf{Q3}&\textbf{max}\\
		\hline
		Sprites with code per project&5.68&1&1&2&5&525\\
		Scripts per project&17.35&1&2&5&12&3038\\
		Number of blocks per project&154.55&1&12&29&76&34622\\
		Blocks in Stage per project&4.80&0&0&0&3&2613\\
		Blocks in Sprites per project&115.57&0&10&26&68&34613\\
		Blocks in Procedures per project&34.17&0&0&0&0&20552\\
		McCabe Cyclomatic Complexity (CC) per script&1.58&1&1&1&1&246\\
		McCabe CC per procedure script&3.75&1&1&2&4&183\\
		Procedures per project with procedures&11.50&1&1&2&6&847\\
		Arguments per Procedure&0.95&0&0&0&1&53\\
		Numerical arguments per procedure with arguments&1.73&0&1&1&2&22\\
		Text arguments per procedure with arguments&0.28&0&0&0&1&24\\
		Boolean arguments per procedure with arguments&0.13&0&0&0&0&14\\
		Calls per procedure&2.14&0&1&1&2&526\\
		Scripts with calls per procedure&1.13&0&1&1&1&59\\
		Variables per project&2.06&0&0&0&1&340\\
		Scripts utilizing variable&4.97&1&1&3&5&1127\\
		Lists per project&0.55&0&0&0&0&319\\
		Conditional statements per project&10.02&0&0&0&3&5950\\
		Recursive loop statements per project&7.65&0&1&2&5&2503\\
		User input blocks per project&4.77&0&0&1&4&1889\\
		Broadcast-receive statements per project&8.57&0&0&0&2&2460\\	
		\hline
	\end{tabular}
	\caption{Summary statistics from the dataset of \nScriptPrograms~non-empty Scratch projects}
	\label{tbl-size}
\end{table*}

@@

Regarding program control features, conditional statements (blocks \texttt{if <condition> then} and \texttt{if <condition> then else}) are used by 39.81\% of the projects. Recursive loops (blocks \texttt{repeat <times>}, \texttt{forever} and \texttt{repeat until <condition>}) are more common, used by 77.18\% of the projects. The most common of the three is the \texttt{forever} block, accounting for 51.86\% of all recursive loops and the least common one is the \texttt{repeat until <condition>} block, accounting for 11.57\% and used in 13.59\% of the total projects.

@@

%user interativity		
\noindent
\fbox{
	\begin{minipage}{0.46\textwidth}
RQ2: One third of the projects use variables, sometimes without initializing them. 39.81\% of the projects contain conditional statements and 77.18\% recursive loops, but conditional recursion is rarely used. More than half of the projects are interactive. 29.57\% of the projects use broadcast and receive blocks, but in 7.99\% of the projects they are not synchronized. Most procedures are called once or twice, from a single script which, in more than half of the cases, is another procedure. Recursive procedure calls exist in 1052 (0.45\% of the total) projects.
	\end{minipage}
}

>>>>

\begin{table*}[ht]
	\centering
	\begin{tabular}{lrrrrrr}
		\hline
		&\textbf{mean}&\textbf{min}&\textbf{Q1}&\textbf{median}&\textbf{Q3}&\textbf{max}\\
		\hline
		Sprites with code per project&5.68&1&1&2&5&525\\
		Scripts per project&17.35&1&2&5&12&3038\\
		Number of blocks per project&154.55&1&12&29&76&34622\\
		Blocks in Stage per project&4.80&0&0&0&3&2613\\
		Blocks in Sprites per project&115.57&0&10&26&68&34613\\
		Blocks in Procedures per project&34.17&0&0&0&0&20552\\
		McCabe Cyclomatic Complexity (CC) per script&1.58&1&1&1&1&246\\
		McCabe CC per procedure script&3.75&1&1&2&4&183\\
		Procedures per project with procedures&11.50&1&1&2&6&847\\
		Arguments per Procedure&0.95&0&0&0&1&53\\
		Numerical arguments per procedure with arguments&1.73&0&1&1&2&22\\
		Text arguments per procedure with arguments&0.28&0&0&0&1&24\\
		Boolean arguments per procedure with arguments&0.13&0&0&0&0&14\\
		Calls per procedure&2.14&0&1&1&2&526\\
		Scripts with calls per procedure&1.13&0&1&1&1&59\\
		Variables per project&2.06&0&0&0&1&340\\
		Scripts utilizing variable&4.97&1&1&3&5&1127\\
		Lists per project&0.55&0&0&0&0&319\\
		Conditional statements per project&10.02&0&0&0&3&5950\\
		Loop statements per project&7.65&0&1&2&5&2503\\
		User input blocks per project&4.77&0&0&1&4&1889\\
		Broadcast-receive statements per project&8.57&0&0&0&2&2460\\	
		\hline
	\end{tabular}
	\caption{Summary statistics from the dataset of \nScriptPrograms~non-empty Scratch projects}
	\label{tbl-size}
\end{table*}

@@

Regarding program control features, conditional statements (blocks \texttt{if <condition> then} and \texttt{if <condition> then else}) are used by 39.81\% of the projects. Loops (blocks \texttt{repeat <times>}, \texttt{forever} and \texttt{repeat until <condition>}) are more common, used by 77.18\% of the projects. The most common of the three is the \texttt{forever} block, accounting for 51.86\% of all loops and the least common one is the \texttt{repeat until <condition>} block, accounting for 11.57\% and used in 13.59\% of the total projects.

@@

%user interativity		
\noindent
\fbox{
	\begin{minipage}{0.46\textwidth}
RQ2: One third of the projects use variables, sometimes without initializing them. 39.81\% of the projects contain conditional statements and 77.18\% contain loops, but conditional loops are rarely used. More than half of the projects are interactive. 29.57\% of the projects use broadcast and receive blocks, but in 7.99\% of the projects they are not synchronized. Most procedures are called once or twice, from a single script which, in more than half of the cases, is another procedure. Recursive procedure calls exist in 1052 (0.45\% of the total) projects.
	\end{minipage}
}
